Restrictive Clearance Comparison

### 2025-01-30 data-raw/RestrictiveClearance_comparison.Rmd
Added relative difference for Css figures and comments to RestrictiveClearance_comparison.Rmd

```{r library_loading}
today <- format(Sys.Date(), "%d%b%Y")
devtools::load_all()
library(tidyverse)
library(ctxR)
library(ggvenn)
library(ggalluvial)
library(flextable)
library(reticulate)
source("data-raw/RC_comparison_bkgd.R") # httk & dawson_2021 loaded here
```

@@

```{r quick-fit}
# Only use plasma for simplicity
this_pk <- pk(cvt %>% filter(conc_medium_normalized == "plasma")) +
  settings_optimx(method = "bobyqa") +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(
    keep_data_original = TRUE,
    suppress.messages = FALSE) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  stat_error_model(error_group = vars(Chemical, Species))

@@

target_chems <- intersect(member_list$cvt, member_list$httk_gas_pbtk)
```

@@

```{r lipinksi_alluvial}
target_chem_summary <- target_chem_info %>%
  distinct(dtxsid, monoisotopicMass, smiles) %>%
  right_join(data.frame(smiles = smiles_list)) %>%
  bind_cols(data.frame(H_donors = py_to_r(py$py_h_donors),
                       H_acceptors = py_to_r(py$py_h_acceptors))
            ) %>%
  left_join(
    target_chem_properties %>%
      filter(source == "ACD/Labs Consensus") %>%
      distinct(dtxsid, source, value)
  ) %>%
  rename(LogKow = value)

@@

all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds)

this_nonflat_winmodel <- get_winning_model(this_pk) %>%
  filter(model %in% c("model_1comp", "model_2comp"))

winning_preds <- predict(this_pk) %>%
  semi_join(this_nonflat_winmodel) %>%
  distinct(Chemical, Species, Chemical_Name,
           model, method, Dose, Media, Route, Reference, pLOQ, Time,
           N_Subjects, Conc, Conc_est)

@@

combined_RMSLE %>%
  ungroup() %>%
  mutate(comparison_group = case_when(
    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
    RMSLE_invivoPKfit > RMSLE_restrictive &
      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than"
  )) %>% 
  ggplot(aes(x = Chemical, y = RMSLE_invivoPKfit)) +
  geom_point(color = "green4") +
  geom_point(aes(y = RMSLE_nonrestrictive), shape = 4, size = 0.5) +
  geom_point(aes(y = RMSLE_restrictive), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = RMSLE_nonrestrictive, ymax = RMSLE_restrictive)) +
  facet_grid(~factor(comparison_group,
                     levels = c("Less than", "Between", "More than")),
             scales = "free_x", space = "free_x") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank())

@@

@@

```{r relative-likelihood}
this_rll_probs <- AIC(this_pk) %>%
  distinct(Chemical, Species, model, AIC) %>%
  pivot_wider(names_from = model, values_from = AIC) %>%
  rowwise() %>% 
  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(across(starts_with("model_"), \(x) {
    signif(exp((minAIC - x)/2) * 100, 4)
  })) %>%
  mutate(across(starts_with("model_"), \(x) {
    ifelse(x < 1E-6, 0, x)
  })) %>%
  inner_join(this_nonflat_winmodel %>% distinct(Chemical, Species, model)) %>%
  ungroup() %>%
  filter(model_1comp >= 99 | model_2comp >= 99,
        model_flat < 1, Chemical %in% target_chems)

@@

```{r combine_tkstats}
# Get the winning model and only include chemicals in target_chems
this_winmodel <- get_winning_model(this_pk) %>%
    filter(Chemical %in% target_chems)
# How many overlapping chemicals have winning models that aren't flat?
count(
  this_winmodel,
  model
) # 153 = 97 1-compartment + 56 2-compartment

this_tkstats <- eval_tkstats(this_pk,
                             model = c("model_1comp", "model_2comp"),
                             finite_only = TRUE,
                             dose_norm = TRUE
) %>%
  rename(CLtot_Fgutabs.tkstats = `CLtot/Fgutabs.tkstats`) %>%
  distinct(Chemical, Species, method, model, Dose, Route, Media,
           CLtot.tkstats, CLtot_Fgutabs.tkstats, halflife.tkstats, Css.tkstats) %>%
  inner_join(this_winmodel)

count(
  this_tkstats,
  # model,
  !is.na(CLtot.tkstats),
  !is.na(CLtot_Fgutabs.tkstats),
  !is.na(halflife.tkstats)
) %>% flextable() %>%
  set_header_labels(
    `!is.na(CLtot.tkstats)` = "Valid Total Clearance",
    `!is.na(CLtot_Fgutabs.tkstats)` = "Valid Total Clearance/Fgutabs",
    `!is.na(halflife.tkstats)` = "Valid halflife",
    n = "Number of Chemicals"
    )
# 46 chemicals have valid total clearance
# 144 chemicals have valid total clearance/Fgutabs
# 5 chemicals have only valid total clearance and no valid total clearance/Fgutabs

@@

this_css_df <- inner_join(
  css_httk_batch(this_param_rest_l, restrictive = TRUE),
  css_httk_batch(this_param_nrest_l, restrictive = FALSE)
) %>%
  inner_join(this_tkstats) %>%
  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
  mutate(comparison_group_Css = factor(
    case_when(
      between(Css.tkstats, Css_httk_r, Css_httk_nr) |
        between(Css.tkstats, Css_httk_nr, Css_httk_r) ~ "Between",
      Css.tkstats < Css_httk_r & Css.tkstats < Css_httk_nr ~ "Below",
      Css.tkstats > Css_httk_r & Css.tkstats > Css_httk_nr ~ "Above"),
    levels = c("Above", "Between", "Below")
  ), Chemical = factor(Chemical) %>% fct_reorder(Css_httk_r)
  )

this_css_df %>%
  ggplot(aes(x = Chemical)) +
  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = Css_httk_r,
                     ymax = Css_httk_nr)
  ) +
  geom_point(aes(y = Css.tkstats, shape = Route), color = "turquoise4") +
  facet_grid(rows = vars(comparison_group_Css),
             scales = "free_x",
             space = "free_x") +
  scale_y_log10(name = "Css") +
  scale_shape_manual(values = c(0,1)) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank())

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Css_comparison_fullChart.png"),
       bg = "white",
       height = 4, width = 8
)

@@

```{r}
this_css_df %>%
  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
  left_join(data.frame(Chemical = names(this_param_rest_l),
                       CLint = vapply(names(this_param_rest_l),
                                      \(x) {
                                        this_param_rest_l[[x]][["Clint"]]
                                      },
                                      FUN.VALUE = numeric(1L)
                       ))) %>%
  mutate(CLint = log10(CLint + 1)) %>%
  ggplot(aes(x = CLint)) +
  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = Css_httk_r,
                     ymax = Css_httk_nr)
  ) +
  scale_y_log10(name = "C<sub>SS</sub>") + 
  labs(x = "CL<sub>int</sub>") +
  geom_point(aes(y = Css.tkstats, shape = Route), color = "turquoise4") +
  scale_shape_manual(values = c(0,1)) +
  theme_bw() +
  theme(axis.title = ggtext::element_markdown())

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Css_x_CLint.png"),
       bg = "white",
       height = 4, width = 8
)
```

@@

```{r weighted_Css}
combined_model_weights %>%
  inner_join(this_css_df) %>%
  ggplot(aes(x = fct_reorder(Chemical, Css_httk_r))) +
  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = Css_httk_r,
                     ymax = Css_httk_nr)
  ) +
  geom_point(aes(y = Css.tkstats, shape = Route, color = gamma_weight)) +
  facet_grid(rows = vars(comparison_group_Css),
             cols = vars(rmsle_comparison_group),
             scales = "free_x",
             space = "free_x") +
  scale_y_log10(name = "Css") +
  scale_shape_manual(values = c(0,1)) +
  scale_color_viridis_b(option = "viridis", 
                        guide = guide_colorbar(position = "bottom")) +
  labs(subtitle = "RMSLE for invivoPKfit compared to httk predictions",
       x = "Chemical\n(ordered by increasing restrictive Css prediction)",
       y = "Css",
       color = "Inverse Confidence") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.subtitle = element_text(hjust = 0.5),
        panel.grid = element_blank(),
        legend.title = element_text(vjust = 0.8))

@@

@@

Notes:
Look at Css values for restrictive/nonrestrictive (httk solutions)
AICs for models

>>>>

```{r library_loading}
today <- format(Sys.Date(), "%d%b%Y")
devtools::load_all()
library(dplyr)
library(tidyr)
library(ggplot2)
library(ctxR)
library(ggvenn)
library(ggalluvial)
library(flextable)
library(reticulate)
library(patchwork)
source("data-raw/RC_comparison_bkgd.R") # httk & dawson_2021 loaded here
```

target_chems <- intersect(member_list$cvt, member_list$httk_gas_pbtk)

filter_targets <- function(.data) {
  stopifnot("Chemical" %in% names(.data))
  dplyr::filter(.data = .data, Chemical %in% target_chems)
}
```

@@

```{r quick-fit}

# Only use plasma for simplicity
this_pk <- pk(cvt %>% 
                dplyr::filter(conc_medium_normalized == "plasma")
              ) +
  settings_optimx(method = "bobyqa") +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(
    keep_data_original = TRUE,
    suppress.messages = FALSE) +
  scale_conc(dose_norm = TRUE, log10_trans = TRUE) +
  stat_error_model(error_group = vars(Chemical, Species))

@@

@@

```{r lipinksi_alluvial}

target_chem_summary <- target_chem_info %>%
  distinct(dtxsid, monoisotopicMass, smiles) %>%
  right_join(data.frame(smiles = smiles_list)) %>%
  bind_cols(data.frame(H_donors = py_to_r(py$py_h_donors),
                       H_acceptors = py_to_r(py$py_h_acceptors))
            ) %>%
  left_join(
    target_chem_properties %>%
      filter(source == "ACD/Labs Consensus") %>%
      distinct(dtxsid, source, value)
  ) %>%
  rename(LogKow = value)

@@

all_httk_preds <- inner_join(restrictive_preds, nonrestrictive_preds) %>%
  filter_targets()

this_nonflat_winmodel <- get_winning_model(this_pk) %>%
  filter(model %in% c("model_1comp", "model_2comp")) %>%
  filter_targets()

winning_preds <- predict(this_pk) %>%
  semi_join(this_nonflat_winmodel) %>% # The targets already filtered here
  distinct(Chemical, Species, Chemical_Name,
           model, method, Dose, Media, Route, Reference, pLOQ, Time,
           N_Subjects, Conc, Conc_est)

@@

combined_RMSLE %>%
  ungroup() %>%
  mutate(comparison_group = case_when(
    between(RMSLE_invivoPKfit, RMSLE_nonrestrictive, RMSLE_restrictive) |
     between(RMSLE_invivoPKfit, RMSLE_restrictive, RMSLE_nonrestrictive) ~ "Between",
    RMSLE_invivoPKfit < RMSLE_nonrestrictive &
      RMSLE_invivoPKfit < RMSLE_restrictive ~ "Less than",
    RMSLE_invivoPKfit > RMSLE_restrictive &
      RMSLE_invivoPKfit > RMSLE_nonrestrictive~ "More than"
  )) %>% 
  ggplot(aes(x = Chemical, y = RMSLE_invivoPKfit)) +
  geom_point(color = "green4") +
  geom_point(aes(y = RMSLE_nonrestrictive), shape = 6, size = 0.5) +
  geom_point(aes(y = RMSLE_restrictive), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = RMSLE_nonrestrictive, ymax = RMSLE_restrictive)) +
  facet_grid(~factor(comparison_group,
                     levels = c("Less than", "Between", "More than")),
             scales = "free_x", space = "free_x") +
  labs(y = "RMSLE") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank())

@@

# Number of chemicals we have RMSLE's for
combined_RMSLE %>% pull(Chemical) %>% unique() %>% length()

@@

```{r relative-likelihood}
this_rll_probs <- AIC(this_pk) %>%
  filter_targets() %>%
  distinct(Chemical, Species, model, AIC) %>%
  pivot_wider(names_from = model, values_from = AIC) %>%
  rowwise() %>% 
  mutate(minAIC = min(c_across(starts_with("model_")), na.rm = TRUE)) %>% 
  ungroup() %>%
  mutate(across(starts_with("model_"), \(x) {
    signif(exp((minAIC - x)/2) * 100, 4)
  })) %>%
  mutate(across(starts_with("model_"), \(x) {
    ifelse(x < 1E-6, 0, x)
  })) %>%
  inner_join(this_nonflat_winmodel %>% distinct(Chemical, Species, model)) %>%
  ungroup() %>%
  filter(model_1comp >= 99 | model_2comp >= 99,
        model_flat < 1, Chemical %in% target_chems)

@@

```{r combine_tkstats}
# Get the winning model and only include chemicals in target_chems
this_winmodel <- get_winning_model(this_pk) %>%
    filter_targets()
# How many overlapping chemicals have winning models that aren't flat?
count(
  this_winmodel,
  model
) # 153 = 97 1-compartment + 56 2-compartment

this_tkstats <- eval_tkstats(this_pk,
                             model = c("model_1comp", "model_2comp"),
                             finite_only = TRUE,
                             dose_norm = TRUE
) %>%
  filter_targets() %>%
  rename(CLtot_Fgutabs.tkstats = `CLtot/Fgutabs.tkstats`) %>%
  distinct(Chemical, Species, method, model, Dose, Route, Media,
           CLtot.tkstats, CLtot_Fgutabs.tkstats, halflife.tkstats, Css.tkstats) %>%
  inner_join(this_winmodel)

count(
  this_tkstats,
  # model,
  !is.na(CLtot.tkstats),
  !is.na(CLtot_Fgutabs.tkstats),
  !is.na(halflife.tkstats)
) %>% flextable() %>%
  set_header_labels(
    `!is.na(CLtot.tkstats)` = "Valid Total Clearance",
    `!is.na(CLtot_Fgutabs.tkstats)` = "Valid Total Clearance/Fgutabs",
    `!is.na(halflife.tkstats)` = "Valid halflife",
    n = "Number of Chemicals"
    )
# 83 chemicals have valid total clearance
# 180 chemicals have valid total clearance/Fgutabs
# 5 chemicals have only valid total clearance and no valid total clearance/Fgutabs

@@

this_css_df <- inner_join(
  css_httk_batch(this_param_rest_l, restrictive = TRUE),
  css_httk_batch(this_param_nrest_l, restrictive = FALSE)
)
# Chart with relative differences (think steps) of Css between clearance types
this_css_df %>%
  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
  count(relative_difference == 0, Css_httk_r == 0) # 31 Chemicals have zero difference
###
this_css_df %>%
  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
  filter(relative_difference > 0) %>%
  ggplot(aes(x = forcats::fct_reorder(Chemical,
                                      relative_difference, .desc = FALSE))) +
  geom_linerange(aes(ymin = Css_httk_nr, ymax = Css_httk_r)) +
  labs(title = "Differences between restrictive & nonrestrictive clearance",
       y = "Css\n(mg/L)", x = "Chemicals") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks = element_blank(),
        panel.grid.major.x = element_blank(),
        plot.title = element_text(hjust = 0.5))

this_css_df %>%
  mutate(relative_difference = log1p(Css_httk_r) - log1p(Css_httk_nr)) %>%
  filter(relative_difference > 0) %>%
  ggplot(aes(x = forcats::fct_reorder(Chemical,
                                      relative_difference))) +
  geom_point(aes(size = relative_difference), y = 0, alpha = 0.2, shape = 16) +
  annotate(x = 1, y = 150 ,label = "Min: 0 mg/L\n31 Chemicals", geom = "text") +
  annotate(x = 140, y = 150 ,label = "Max: 30 mg/L\n", geom = "text") +
  scale_y_continuous(limits = c(-150,150)) +
  scale_size_area(max_size = 40) +
  coord_cartesian(clip = "off") +
  theme_void() +
  theme(legend.position = "none",
        plot.margin = unit(c(2,2,1,2), units = "inches"))

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Css_difference_httk_inkblot.png"),
       bg = "white",
       height = 5, width = 7)
###

this_css_df <- this_css_df %>%
  inner_join(this_tkstats) %>%
  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats) %>%
  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
  mutate(comparison_group_Css = factor(
    case_when(
      between(Css.tkstats, Css_httk_r, Css_httk_nr) |
        between(Css.tkstats, Css_httk_nr, Css_httk_r) ~ "Between",
      Css.tkstats < Css_httk_r & Css.tkstats < Css_httk_nr ~ "Below",
      Css.tkstats > Css_httk_r & Css.tkstats > Css_httk_nr ~ "Above"),
    levels = c("Above", "Between", "Below")
  ), Chemical = factor(Chemical) %>% forcats::fct_reorder(Css_httk_r)
  ) %>%
  mutate(nearest_clearance = factor(
    case_when(
      between(log2(Css.tkstats),
              log2(Css_httk_r)-1, log2(Css_httk_r)+1) |
        (comparison_group_Css == "Above" &
           log2(Css.tkstats) <= log2(Css_httk_r)+2) ~ "Restrictive",
      between(log2(Css.tkstats),
              log2(Css_httk_nr)-1, log2(Css_httk_nr)+1) |
        comparison_group_Css == "Below" ~ "NonRestrictive",
      .default = "Out of Range"
    )
  ))

this_css_df %>%
  ggplot(aes(x = Chemical)) +
  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = Css_httk_r,
                     ymax = Css_httk_nr)
  ) +
  geom_point(aes(y = Css.tkstats, shape = Route,
                 color = nearest_clearance)) +
  facet_grid(rows = vars(comparison_group_Css),
             scales = "free_x",
             space = "free_x") +
  scale_y_log10(name = "Css") +
  scale_shape_manual(values = c(0,1)) +
  scale_color_manual(values = c("magenta3", "green4", "black"),
                     name = "Within 2-fold\nof clearance:",
                     ) +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        panel.grid = element_blank()) +
  guide_area() +
  plot_layout(widths = c(8,1))

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Css_comparison_2foldclearancefullChart.png"),
       bg = "white",
       height = 5, width = 10
)

this_css_df %>% 
  group_by(Chemical) %>%
  count(nearest_clearance) %>%
  filter(nearest_clearance != "Out of Range") %>% View()

@@

Overwhelmingly, the results of this is a Restrictive clearance model...
however it is important to flag

```{r Css_CLint}
this_css_clint_df <- this_css_df %>%
  distinct(Chemical, model, Route, Css_httk_r, Css_httk_nr, Css.tkstats,
           nearest_clearance, comparison_group_Css) %>%
  filter(Css_httk_nr > 0, Css_httk_r > 0, Css.tkstats > 0) %>%
  left_join(data.frame(Chemical = names(this_param_rest_l),
                       CLint = vapply(names(this_param_rest_l),
                                      \(x) {
                                        this_param_rest_l[[x]][["Clint"]]
                                      },
                                      FUN.VALUE = numeric(1L)
                       ))) %>%
  dplyr::filter(CLint > 0)

this_css_clint_df %>%
  left_join(target_chem_lipinski %>% rename(Chemical = dtxsid)) %>%
  ggplot(aes(x = CLint)) +
  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = Css_httk_r,
                     ymax = Css_httk_nr)
  ) +
  scale_y_log10(name = "C<sub>ss</sub>") + 
  scale_x_log10(name = "CL<sub>int</sub>") +
  geom_point(aes(y = Css.tkstats, 
                 fill = `Mass <= 500 Da`,
                 shape = Route,
                 color = nearest_clearance)) +
  facet_grid(rows = vars(nearest_clearance)) +
  scale_color_manual(values = c("magenta3", "green4", "black"),
                     guide = "none") +
  scale_shape_manual(values = c(21,22)) +
  scale_fill_manual(values = c("white", "grey5")) +
  guides(fill = guide_legend(override.aes = list(shape = 21))) +
  theme_bw() +
  theme(axis.title = ggtext::element_markdown())

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "Css_x_CLint_wNearestClearanceGrid.png"),
       bg = "white",
       height = 6, width = 10
)

this_css_clint_df %>%
  # group_by(Route) %>%
  group_modify(~broom::tidy(lm(Css.tkstats ~ nearest_clearance + CLint, data = .x)))

@@

```{r weighted_Css}
combined_model_weights %>%
  inner_join(this_css_df) %>%
  filter_targets() %>%
  ggplot(aes(x = forcats::fct_reorder(Chemical, Css_httk_r))) +
  geom_point(aes(y = Css_httk_r), shape = 4, size = 0.5) +
  geom_point(aes(y = Css_httk_nr), shape = 4, size = 0.5) +
  geom_linerange(aes(ymin = Css_httk_r,
                     ymax = Css_httk_nr)
  ) +
  geom_point(aes(y = Css.tkstats, shape = Route, color = gamma_weight)) +
  facet_grid(rows = vars(comparison_group_Css),
             cols = vars(rmsle_comparison_group),
             scales = "free_x",
             space = "free_x") +
  scale_y_log10(name = "Css") +
  scale_shape_manual(values = c(0,1)) +
  scale_color_viridis_b(option = "viridis") +
  labs(subtitle = "RMSLE for invivoPKfit compared to httk predictions",
       x = "Chemical\n(ordered by increasing restrictive Css prediction)",
       y = "Css",
       color = "Inverse Confidence") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.subtitle = element_text(hjust = 0.5),
        panel.grid = element_blank(),
        legend.title = element_text(vjust = 0.8)) +
  guide_area() +
  plot_layout(widths = c(8,1))

@@

First, there are about 80 chemicals which have a `CLtot.tkstats` which may
give us some idea of the clearance alongside the _inverse confidence_ metric.

```{r CLtot_subset}

this_tkstats %>%
  inner_join(this_httk_clearance_df) %>%
  inner_join(combined_model_weights) %>%
  filter(!is.na(CLtot.tkstats)) %>%
  mutate(comparison_CLtot = factor(
    case_when(
    between(log2(CLtot.tkstats), 
            log2(restrictive_clearance)-1,
            log2(restrictive_clearance)+1) ~ "Restrictive",
    between(log2(CLtot.tkstats), 
            log2(nonrestrictive_clearance)-1,
            log2(nonrestrictive_clearance)+1) ~ "Nonrestrictive",
    between(CLtot.tkstats,
            restrictive_clearance, nonrestrictive_clearance) ~ "Between",
    .default = "Out of Range"
  ), levels = c("Nonrestrictive", "Between", "Restrictive", "Out of Range")
  )) %>%
  ggplot(aes(forcats::fct_reorder(Chemical,
                          gamma_weight))) +
  geom_point(aes(y = CLtot.tkstats, fill = gamma_weight),
             shape = 21) +
  geom_linerange(aes(ymin = restrictive_clearance, 
                     ymax = nonrestrictive_clearance)) +
  geom_point(aes(y = restrictive_clearance),
             shape = 2, size = 0.8) + # Note that this is the lower value
  geom_point(aes(y = nonrestrictive_clearance),
             shape = 6, size = 0.8) +
  scale_fill_viridis_b(option = "viridis", 
                        guide = guide_colorbar(position = "bottom"),
                       limits = c(0,1.5)) +
  scale_y_log10() +
  facet_grid(cols = vars(comparison_CLtot),
             scales = "free_x",
             space = "free_x") +
  labs(y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.subtitle = element_text(hjust = 0.5),
        legend.title = element_text(vjust = 0.8))

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "TotalClearance_withRMSLEweights.png"),
       bg = "white",
       height = 4, width = 8
)

```{r CLtot_subset_withCss}

this_tkstats %>%
  inner_join(this_httk_clearance_df) %>%
  inner_join(combined_model_weights) %>%
  left_join(this_css_df) %>%
  filter(!is.na(CLtot.tkstats)) %>%
  mutate(comparison_CLtot = factor(
    case_when(
      between(log2(CLtot.tkstats),log2(restrictive_clearance)-1,
              log2(restrictive_clearance)+1) ~ "Restrictive",
      between(log2(CLtot.tkstats),log2(nonrestrictive_clearance)-1,
              log2(nonrestrictive_clearance)+1) ~ "Nonrestrictive",
      between(CLtot.tkstats,
              restrictive_clearance, nonrestrictive_clearance) ~ "Between",
      .default = "Out of range"
  ), levels = c("Nonrestrictive", "Between", "Restrictive", "Out of range"))) %>%
  ggplot(aes(forcats::fct_reorder(Chemical,
                          gamma_weight))) +
  geom_point(aes(y = CLtot.tkstats, fill = gamma_weight),
             shape = 21) +
  geom_linerange(aes(ymin = restrictive_clearance, 
                     ymax = nonrestrictive_clearance)) +
  geom_point(aes(y = restrictive_clearance),
             shape = 4, size = 0.8) + # Note that this is the lower value
  geom_point(aes(y = nonrestrictive_clearance),
             shape = 4, size = 0.8) +
  scale_fill_viridis_b(option = "viridis", 
                        guide = guide_colorbar(position = "bottom")) +
  scale_y_log10() +
  facet_grid(cols = vars(comparison_CLtot),
             scales = "free_x") +
  labs(y = "Total Clearance", x = "Chemical", fill = "Inverse Confidence",
       subtitle = "Estimates within 20% of in vitro modelled predictions") +
  theme_bw() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        plot.subtitle = element_text(hjust = 0.5),
        legend.title = element_text(vjust = 0.8))

ggsave(filename = paste0(Sys.getenv("FIG_DIR"),
                         "RestrictiveClearance_Analysis/",
                         "CURRENT_", "TotalClearance_withRMSLEweights.png"),
       bg = "white",
       height = 4, width = 8
)

@@

## Notes:
Look at Css values for restrictive/nonrestrictive (httk solutions)
AICs for models
Important to look for potential reflective metrics and find associations 
(CLtot, Css, fup) and also look at physiochemical properties that may create
some distinctions once a prediction of clearance type is made.

So the model will be something like `CLtot ~ Css + fup + Clearance_Type + GFR`
and we can re-simplify certain things into `halflife` and `kelim` to see
how likely this would be in a simple, classical PK model.
